Exploratory data analysis

### 2019-06-21 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE)

      fv_nri_car, fv_nri_info.gain, fv_nri_gain.ratio,
      fv_nri_rank, fv_nri_cor,
      fv_nri_mrmr,
      fv_nri_cmim, fv_nri_var,

      fv_vi_car, fv_vi_info.gain, fv_vi_gain.ratio,
      fv_vi_rank, fv_vi_cor,
      fv_vi_mrmr,
      fv_vi_cmim, fv_vi_var,

      fv_hr_car, fv_hr_info.gain, fv_hr_gain.ratio,
      fv_hr_rank, fv_hr_cor,
      fv_hr_mrmr,
      fv_hr_cmim, fv_hr_var
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
```

@@

fv_all = dplyr::bind_rows(fv_vi_car$data, 
                          fv_vi_info.gain$data, 
                          fv_vi_gain.ratio$data,
                          fv_vi_rank$data, 
                          fv_vi_cor$data, 
                          fv_vi_mrmr$data, 
                          fv_vi_cmim$data, 
                          fv_vi_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:89, 8)) %>% 
  tidyr::spread(method, value) %>% 
  mutate_if(is.numeric, list(~na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

@@

fv_all = dplyr::bind_rows(fv_nri_car$data, 
                          fv_nri_info.gain$data, 
                          fv_nri_gain.ratio$data,
                          fv_nri_rank$data, 
                          fv_nri_cor$data, 
                          fv_nri_mrmr$data, 
                          fv_nri_cmim$data, 
                          fv_nri_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:7381, 8)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

@@

ggcorrplot(corr,
           #p.mat = p.mat,
           hc.order = TRUE,
           type = "lower",
           lab = TRUE)
```

@@

fv_all = dplyr::bind_rows(fv_hr_car$data, 
                          fv_hr_info.gain$data, 
                          fv_hr_gain.ratio$data,
                          fv_hr_rank$data, 
                          fv_hr_cor$data, 
                          fv_hr_mrmr$data, 
                          fv_hr_cmim$data, 
                          fv_hr_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:122, 8)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

>>>>

      fv_nri_car, fv_nri_info.gain, fv_nri_gain.ratio,
      fv_nri_symuncert, fv_nri_relief,
      fv_nri_rank, fv_nri_cor,
      fv_nri_mrmr,
      fv_nri_cmim, fv_nri_var,

      fv_vi_car, fv_vi_info.gain, fv_vi_gain.ratio,
      fv_vi_symuncert, fv_vi_relief,
      fv_vi_rank, fv_vi_cor,
      fv_vi_mrmr,
      fv_vi_cmim, fv_vi_var,

      fv_hr_car, fv_hr_info.gain, fv_hr_gain.ratio,
      fv_hr_symuncert, fv_hr_relief,
      fv_hr_rank, fv_hr_cor,
      fv_hr_mrmr,
      fv_hr_cmim, fv_hr_var
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
```

@@

fv_all = dplyr::bind_rows(fv_vi_car$data, 
                          fv_vi_info.gain$data, 
                          fv_vi_gain.ratio$data,
                          fv_vi_symuncert$data,
                          fv_vi_relief$data,
                          fv_vi_rank$data, 
                          fv_vi_cor$data, 
                          fv_vi_mrmr$data, 
                          fv_vi_cmim$data, 
                          fv_vi_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:89, 10)) %>% 
  tidyr::spread(method, value) %>% 
  mutate_if(is.numeric, list(~na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

@@

fv_all = dplyr::bind_rows(fv_nri_car$data, 
                          fv_nri_info.gain$data, 
                          fv_nri_gain.ratio$data,
                          fv_nri_symuncert$data,
                          fv_nri_relief$data,
                          fv_nri_rank$data, 
                          fv_nri_cor$data, 
                          fv_nri_mrmr$data, 
                          fv_nri_cmim$data, 
                          fv_nri_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:7381, 10)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

@@

ggcorrplot(corr,
           #p.mat = p.mat,
           hc.order = FALSE,
           type = "lower",
           lab = TRUE)
```

@@

fv_all = dplyr::bind_rows(fv_hr_car$data, 
                          fv_hr_info.gain$data, 
                          fv_hr_gain.ratio$data,
                          fv_hr_symuncert$data,
                          fv_hr_relief$data,
                          fv_hr_rank$data, 
                          fv_hr_cor$data, 
                          fv_hr_mrmr$data, 
                          fv_hr_cmim$data,
                          fv_hr_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:122, 10)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)
